Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2018-08-14 paper/ms.tex
Updated the text with text from Carlyn.

There has been debate over what triggers a WD explosion. One of the primary
ideas is the single degenerate process. During this process the white dwarf
accretes material from a giant companion. Once the white dwarf reaches the
Chandrasekhar limit, the star is consumed by thermonuclear runaway and
explodes.

@@

@@

We used MESA, a 1-D stellar evolution code, to create the hybrid model.

We found that the most abundant isotopes in the model were C12, O16, Ne20.
There were a few other isotopes that were added to form Ne22 later. We saw
that  ...

@@

In order to see where we should ignite the flame, we plotted the temperature
profile. It was found that the peak temperature is at the center of the
star, therefore, it was obvious to ignite the flame in the core.

@@

We mapped our hybrid model to the FLASH grid. In order to convert our 1-D
MESA model into FLASH, which is a 2-D code, we needed the ratio of neutrons
to protons in the nuclei to be the same ratio as in the mesa profile. This is
because the amount of extra neutrons around is important when burning the
star because that determines how much neutron rich isotopes the burring
produces.

@@

@@

@@

>>>>

 There has been debate over what triggers a WD explosion. One of the
 primary ideas is the single degenerate process. During this process
 the white dwarf accretes material from a giant companion. Once the
 white dwarf reaches the Chandrasekhar limit, the star is consumed
 by thermonuclear runaway and explodes. Another idea is the double
 degenerate process: two white dwarfs merge to exceed the Chandrasekhar
 limit. Hydrogen is not expected to be observed since both stars exhausted
 their hydrogen long ago.

@@

A deflagration alone will not produce an event of normal
brightness and expansion velocity. Instead, the initial
deflagration must transition to a detonation after the star has
expanded some in order to produce abundances and a stratified
ejecta in keeping with observations. The physics of this
“deflagration-to- detonation transition” (DDT) are not
completely understood, but there has been considerable study
based on mechanisms involving flame fronts in highly turbulent
conditions. These models generally reproduce the observations
under certain assumptions about the ignition, but research has
shown that the results are very sensitive to the details of the
ignition. In our simulations, we initialize a detonation once
the deflagration front reaches a characteristic DDT fuel density,
which controls the degree of expansion the star undergoes during
the deflagration stage.

The comparison study of tradition C/O progenitor WDs used the same initial
conditions for the realizations within the suite. The traditional models
are simulated with the same code and the same set of perturbations on the
initial match head (realization). The only difference is the different
nuclear burning to include the other Ne and the initial profile of the
1-d model.

@@

We used MESA, a 1-D stellar evolution code, to create the hybrid
model. We made the hybrid model have the same central temperature
and density as the classic model.

We found that the most abundant isotopes in the model were C12, O16,
Ne20. There were a few other isotopes that were added to form Ne22
later. We saw that  ….

@@

In order to see where we should ignite the flame, we plotted the
temperature profile. It was found that the peak temperature is at the
center of the star, therefore, it was obvious to ignite the flame in
the core. (PUT IN TEMP PROFILE)

@@

We mapped our hybrid model to the FLASH grid. In order to convert our 1-D
MESA model into FLASH, which is a 2-D code, we needed symmetric nuclear
matter. This means that the ratio of neutrons to protons in the nuclei
must be the same ratio as in the mesa profile. This is because the amount
of extra neutrons around is important when burning the star because that
determines how much neutron rich isotopes the burning produces.

@@

----updated text-----

DDT Process:
The fuel starts off cold. The elections in the plasma conduct heat
and the fuel begins to heat up. Once the fuel reaches a certain
temperature, the reaction starts. The fuel abundance begins to
decline because it is consuming fuel. Energy is produced which
makes the fuel hot. Eventually, all that’s left is ash. As
surface area grows, conducted energy increases and density
decreases. At low densities Rayleigh-Taylor instability causes
the flame to get more tangled and unstable. Eventually, the
star will get a large enough surface area in this volume that
the net burning effect is supersonic. Therefore, the transition
from deflagration to detonation is made.

A deflagration alone will not produce an event of normal
brightness and expansion velocity. Instead, the initial
deflagration must transition to a detonation after the star has
expanded some in order to produce abundances and a stratified
ejecta in keeping with observations. The physics of this
“deflagration-to- detonation transition” (DDT) are not
completely understood, but there has been considerable study
based on mechanisms involving flame fronts in highly turbulent
conditions. These models generally reproduce the observations
under certain assumptions about the ignition, but research has
shown that the results are very sensitive to the details of the
ignition. In our simulations, we initialize a detonation once
the deflagration front reaches a characteristic DDT fuel density,
which controls the degree of expansion the star undergoes during
the deflagration stage.

The comparison study of tradition C/O progenitor WDs used the same initial
conditions for the realizations within the suite. The traditional models
are simulated with the same code and the same set of perturbations on the
initial match head (realization). The only difference is the different
nuclear burning to include the other Ne and the initial profile of the
1-d model.

----above updated text-----

@@

This is a plot of the estimated Ni56 yield vs. mass below 2e7 g/cc at
the time of the DDT.

The degree of expansion was found using the time at which the first
detonation point occurred, and the mass at density less then 2e7 g/cc. The
estimated Ni56 Yield is the final estimated mass of the model.

@@

The conversion of Ni56 to Iron group elements are more pronounced in my
case. There are two assumptions as to why figure 6 is more pronounced
in my paper then in Dons.  First is that higher critical density leads
to higher electron capture resulting in less Ni56 produced. The second
is that the central ignition leads to early burning at higher density.

As the star burns mass, the surface area grows, resulting in a decrease
in density. The results show that the models that burned less mass during
the deflagration phase, expand less, produce more Ni-56. This is because
the density rich mass the model has at the DDT point is the ‘fuel’
it needs to produce Ni-56. Therefore, the more mass, the more Ni-56. On
average, the CO model, shown in figure 4, reaches the DDT faster then
the hybrid model. Figures 3 and 4 show that the hybrid model has a wider
range of estimated Ni-56 mass suggesting a greater range of burned mass
and expansion during the deflagration phase.
